Automated troubleshooting toolset for SDNs

### 2013-10-26 draft.tex
better conclusion section 2

Thanks to the SDN stack, one can first build a tool to check consistency between state layers in order to identify on which part of the network architecture a bug is happening (in which \textit{code layer}). Then, when the layer is identified, an other tool take over to localize the issue inside the code layer. We will see in section \ref{Network Troubleshooting - Tools} which kind of tools could be used to handle this bug hunting inside the code layer.

>>>>

Thanks to the SDN stack, one can first build a tool to check consistency between state layers in order to identify on which part of the network architecture a bug is happening (in which \textit{code layer}). Then, when the layer is identified, an other tool take over to localize the issue inside the code layer. We will see in section \ref{Network Troubleshooting - Tools} which kind of tools could be used to handle this bug hunting. Tools to find the code layer concerned by the issue and tools which operate inside the code layer, to find the cause of the bug.
